Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex
minor corrections

More formally, a constraint $c_1(G_1, ... G_n)$ \textit{implies} another constraint~$c_2(G'_1, ..., G'_m)$ whenever
the statement $\forall G_i, G'_j : c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$ holds. To simplify testing,
we shall only consider {\em range-restricted} implications, that is, we shall require that $\{G'_1, ..., G'_m\} \subseteq \{G_1, ..., G_n\}$.
To simplify notation, and in line with logic programming, we shall often make the quantification implicit and simply write this as rules $ c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$.  We say that the first constraint is more specific than the second, and the second is more general.

@@

\paragraph{Example}
Consider the following implication:
$$PERMUTATION(G) \rightarrow ALLDIFFERENT(G)$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $ALLDDIFFERENT(G)$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@

Two constraints are \textit{equivalent} if they imply one another. %More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n) \leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = SUM(H)$ with $size(H) = 2$ and $G_2 \subset H, G_3 \subset H$.
\luc{Do we really need this, or can we write it in a real equivalence --- conjunctive formula?}

@@

Redundant constraints can be reduced in different ways.
Duplications should be detected in a post-processing step that uses entailment or heursitics to filter constraints.
Accidental constraints may be detected through heuristics, however, they can be also be removed by adding additional data.

>>>>

More formally, a constraint $c_1(G_1, ... G_n)$ \textit{implies} another constraint~$c_2(G'_1, ..., G'_m)$ whenever
the  following statement holds: $$\forall G_i, G'_j : c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m).$$

We shall only consider {\em range-restricted} implications, that is, we shall require that $\{G'_1, ..., G'_m\} \subseteq \{G_1, ..., G_n\}$.
To simplify notation, and in line with logic programming, we shall often make the quantification implicit and simply write this as rules $ c_1(G_1, ... G_n) \rightarrow c_2(G'_1, ... G'_m)$.  We say that the first constraint is more specific than the second, and the second is more general.

@@

\paragraph{Example}
Consider the following implication:
$$\ecperm{G} \rightarrow \ecalldiff{G}$$
(it can be seen in Table~\ref{table:constraints} that both constraints only hold if $G$ is a vector).
In this case the arguments are identical in both constraints.
Given that the problem is to find the set of {\em all} constraints, and that the more general constraint is entailed
by the more specific one, the $ALLDDIFFERENT(G)$ constraint will be {\em redundant}.
So, for most applications, it will be sufficient to output only the most specific one.

@@

Two constraints are \textit{equivalent} if they imply one another. %More formally, $\forall G'_1, ..., G'_n$ s.t. $\{G''_1, ..., G''_n\} = \{G'_1, ..., G'_n\},\, c_1(G'_1, ... G'_n) \leftrightarrow c_2(G''_1, ..., G''_n)$.
An example within the same \template is for the sum over vectors constraint: $G_1 = +(G_2, G_3) \leftrightarrow G_1 = +(G_3, G_2)$. A related example over multiple constraints is $G_1 = +(G_2, G_3) \leftrightarrow G_1 = \textit{SUM}(H)$ with $\textit{size}(H) = 2$ and $G_2 \subset H, G_3 \subset H$.
\luc{Do we really need this, or can we write it in a real equivalence --- conjunctive formula?}

@@

Redundant constraints can be reduced in different ways.
Duplications should be detected in a post-processing step that uses entailment or heuristics to filter constraints.
Accidental constraints may be detected through heuristics, however, they can be also be removed by adding additional data.
